Supplementary information

### 2016-12-20 Supplementary information.tex
Last changes before moving to different location

  \topcaption {Statistical regression models for AGB. When log is the natural logarithm; AGB is the above ground biomass (Mg/ha); BIO9 is the mean temperature of driest quarter (\textcelsius); BIO16 is the precipitation of the wettest quarter (mm); EVI is the enhanced vegetation index; Lat is the absolute value of latitude (decimal degrees);  n is the number of observations; R\textsubscript{a}\textsuperscript{2} is the adjusted coefficient of determination; MSE is the mean squared error; F is the F-statistic calculated; AIC is the akaike information criterion }  % requires the topcapt package

@@

       Model  & n & R\textsubscript{a}\textsuperscript{2} & MSE & F & AIC\\

@@

    $(1)AGB=-1.028\textsuperscript{e+03}+2.011\textsuperscript{e+00}BIO10+1.545\textsuperscript{e+00}BIO11-6.329\textsuperscript{e-03}BIO16+5.881\textsuperscript{e-02}BIO17+3.903\textsuperscript{e+02}EVI$&41&0.2164 &3331&3.21&456.41885\\
    $(2)AGB=-1.876\textsuperscript{e+03}+7.766\textsuperscript{e+00}BIO1+7.64\textsuperscript{e-02}BIO4+5.413\textsuperscript{e-03}BIO12-2.908\textsuperscript{e-00}BIO15$&43&-0.0278&4338&0.72&488.84983\\
    $(3)AGB=-1.152\textsuperscript{e+03}+4.167\textsuperscript{e+00}BIO1+9.011\textsuperscript{e-02}BIO4+2.871\textsuperscript{e-03}BIO12-1.175\textsuperscript{e+00}BIO15+3.770\textsuperscript{e+02}EVI$&41&0.2261&3290&3.34&455.90772\\    
    $(4)AGB=-1.241\textsuperscript{e+03}-3.911\textsuperscript{e+01}Lat+4.759\textsuperscript{e+00}BIO10+1.202\textsuperscript{e+00}BIO11-1.017\textsuperscript{e-01}BIO16+7.924\textsuperscript{e-02}BIO17+2.904\textsuperscript{e+02}EVI$&41&0.2218&3308&2.90&456.94720\\   
    $(5)AGB=-1.372\textsuperscript{e+03}+6.358\textsuperscript{e+00}BIO10+1.789\textsuperscript{e+00}BIO11-7.389\textsuperscript{e-02}BIO16-1.229\textsuperscript{e-01}BIO17-7.746\textsuperscript{e+01}Lat$&43&0.154&3571&2.53&481.33332\\   
    $(6)AGB=-1.286\textsuperscript{e+03}-9.594\textsuperscript{e+01}Lat+8.621\textsuperscript{e+00}BIO1+1.161\textsuperscript{e-01}BIO4-6.145\textsuperscript{e-02}BIO12-4.687\textsuperscript{e-01}  BIO15$&43&0.1819&3453&2.87&479.89058\\    
$(7)AGB=-1.099\textsuperscript{e+03}-4.978\textsuperscript{e+01}Lat+5.863\textsuperscript{e+00}BIO1+1.100\textsuperscript{e-01}BIO4-3.161\textsuperscript{e-02}BIO12-5.549\textsuperscript{e-01}BIO15+2.529\textsuperscript{e+02}EVI$&41&0.2405&3229&3.11&455.94975\\

@@

$(11)AGB=-1.693\textsuperscript{e+03}-2.897\textsuperscript{e+01}Lat+7.567\textsuperscript{e+00}BIO9-4.108\textsuperscript{e-02}BIO17$&43&0.2072&3346&4.66&476.80085\\
$(12)AGB=-1.485\textsuperscript{e+03}-1.662\textsuperscript{e+00}Lat+5.443\textsuperscript{e+00}BIO9+5.658\textsuperscript{e-02}BIO17+2.770\textsuperscript{e+02}EVI$&41&0.2755&3080&4.80&452.36112\\

@@

$(21)AGB=4.173\textsuperscript{e+04}-1.606\textsuperscript{e+02}\frac{BIO11}{10}-4.733\textsuperscript{e-02}BIO16+1.602\textsuperscript{e+02}\frac{BIO9}{10}-3.083\textsuperscript{e+03}\frac{BIO1}{10}+5.685\textsuperscript{e+01}(\frac{BIO1}{10})^2+2.826\textsuperscript{e+02}EVI$&41&0.3096&2935&3.99&452.03760\\
$(22)AGB=-3.485\textsuperscript{e+02}+1.954\textsuperscript{e-03}BIO10^2+3.104\textsuperscript{e-03}BIO11^2-6.339\textsuperscript{e-05}BIO16^2+3.609\textsuperscript{e-04}BIO17^2+5.595\textsuperscript{e+02}EVI^2$&41&0.233&3261&3.43&455.54124\\

@@

$(29)\frac{1}{AGB}=1.763\textsuperscript{e-01}-6.966\textsuperscript{e-04}BIO9+3.451\textsuperscript{e-05}BIO16-1.008\textsuperscript{e-01}EVI+5.315\textsuperscript{e-03}|Lat|$&41&0.1325&0.0014&2.53&-147.62232\\

@@

$(32)\log{AGB}=-1.615\textsuperscript{e+01}+7.970\textsuperscript{e-02}\log{BIO9}-3.738\textsuperscript{e-04}\log{BIO16}+2.816\textsuperscript{e+00}\log{EVI}-2.259\textsuperscript{e-01}|Lat|$&41&0.3193&0.508&5.69&95.26750\\

@@

$(35)\sqrt{AGB}=-7.719\textsuperscript{e+01}+3.201\textsuperscript{e-01}BIO9-7.403\textsuperscript{e-05}BIO16+1.253\textsuperscript{e+01}EVI-5.965\textsuperscript{e-01}|Lat|$&41&0.3357&7.53&6.05&205.81366\\

>>>>

  \topcaption {Statistical regression models for AGB. When log is the natural logarithm; AGB is the above ground biomass (Mg/ha); BIO9 is the mean temperature of driest quarter (\textcelsius); BIO10 mean temperature of warmest quarter (\textcelsius); BIO11 mean temperature of coldest quarter (\textcelsius); BIO16 is the precipitation of the wettest quarter (mm); EVI is the enhanced vegetation index; Lat is the absolute value of latitude (decimal degrees);  n is the number of observations; R$_a^2$  is the adjusted coefficient of determination; MSE is the mean squared error; F is the F-statistic calculated; AIC is the akaike information criterion }  % requires the topcapt package

@@

       Model  & n & R$_{a}^{2}$ & MSE & F & AIC\\

@@

    $(1)AGB=-2.210$^{e+03}$+2.946\$^{e+00}$BIO10+4.687$^{e+00}$BIO11+2.108${e-01}$BIO16-2.334$^{e-01}$BIO17+2.465$^{e+02}$EVI$&40&0.04163 &4157&1.34&\\
    $(2)AGB=-1.876$^{e+03}$+7.766$^{e+00}$BIO1+7.64$^{e-02}$BIO4+5.413$^{e-03}$BIO12-2.908$^{e-00}$BIO15$&43&-0.0278&4338&0.72&\\
    $(3)AGB=-3.260$^{e+03}$+1.233$^{e+01}$BIO1+1.61$^{e-01}$BIO4+1.934$^{e-02$}BIO12-3.805$^{e+00}$BIO15+2.835$^{e+02}$EVI$&40&0.07695&4003&1.65&\\    
    $(4)AGB=-1.920$^{e+03}$-7.292$^{e+01}$Lat+7.878$^{e+00}$BIO10+1.846$^{e+00}$BIO11-1.115$^{e-01}$BIO16+2.404$^{e-02}$BIO17+1.561$^{e-02}$EVI$&40&0.1288&3779&1.961&\\   
    $(5)AGB=-1.372$^{e+03}$+6.358$^{e+00}$BIO10+1.789$^{e+00}$BIO11-7.389$^{e-02}$BIO16-1.229$^{e-01}$BIO17-7.746$^${e+01}Lat$&43&0.154&3571&2.529&\\   
    $(6)AGB=-1.286$^{e+03}$-9.594$^{e+01}$Lat+8.621$^{e+00}$BIO1+1.161$^{e-01}$BIO4-6.145$^{e-02}$BIO12-4.687$^{e-01}$BIO15$&43&0.1819&3453&2.868&\\    
$(7)AGB=-2.219$^{e+03}$-7.703$^{e+01}$Lat+1.113$^{e+00}$BIO1+1.885$^{e-01}$BIO4-4.071$^{e-02}$BIO12-1.735$^{e-01}$BIO15+1.813$^{e+02}$EVI$&41&0.1762&3573&2.39&\\

@@

$(11)AGB=-1.693$^{e+03}$-2.897$^{e+01}$Lat+7.567$^{e+00}$BIO9-4.108$^{e-02}$BIO17$&43&0.2072&3346&4.66&476.80085\\
$(12)AGB=-1.485$^{e+03}$-1.662$^{e+00}$Lat+5.443$^{e+00}$BIO9+5.658$^{e-02}$BIO17+2.770$^{e+02}$EVI$&41&0.2755&3080&4.80&452.36112\\

@@

$(21)AGB=4.173$^{e+04}$-1.606$^{e+02}$\frac{BIO11}{10}-4.733$^{e-02}$BIO16+1.602$^{e+02}$\frac{BIO9}{10}-3.083$^{e+03}$\frac{BIO1}{10}+5.685$^{e+01}$(\frac{BIO1}{10})^2+2.826$^{e+02}$EVI$&41&0.3096&2935&3.99&452.03760\\
$(22)AGB=-3.485$^{e+02}$+1.954$^{e-03}$BIO10^2+3.104$^{e-03}$BIO11^2-6.339$^{e-05}$BIO16^2+3.609$^{e-04}$BIO17^2+5.595$^{e+02}$EVI^2$&41&0.233&3261&3.43&455.54124\\

@@

$(29)\frac{1}{AGB}=1.763$^{e-01}$-6.966$^{e-04}$BIO9+3.451$^{e-05}$BIO16-1.008$^t{e-01}$EVI+5.315$^{e-03}$|Lat|$&41&0.1325&0.0014&2.53&-147.62232\\

@@

$(32)\log{AGB}=-1.615$^{e+01}$+7.970$^{e-02}$\log{BIO9}-3.738$^{e-04}$\log{BIO16}+2.816$^{e+00}$\log{EVI}-2.259$^{e-01}$|Lat|$&41&0.3193&0.508&5.69&95.26750\\

@@

$(35)\sqrt{AGB}=-7.719$^{e+01}$+3.201$^{e-01}$BIO9-7.403$^{e-05}$BIO16+1.253$^{e+01}$EVI-5.965$^{e-01}$|Lat|$&41&0.3357&7.53&6.05&205.81366\\
